\chapter*{Acknowledgements}
\thispagestyle{empty}

I thank my mom Maritza Badilla, my dad Ricardo Guindon, my sister Hazel, my brother David, the extended Guindon and Badilla families, and the Monteverde community, which all have conspired to provide the perfect environment for maximum development in both artistic endeavor and scientific enterprise.

I thank Elena $\heartsuit$, for sharing her support during the development of this project.

I thank my close highschool friends Diego, Cristina, and Josue, for stubbornly distracting me from my research. I know you all were acting in my best interests, or so you all say.

I thank my close college friend Emi, my close friends at the SeleHouse, my friends at TEC, and my friends at RidgeRun, which have all provided spaces where I've shared my research's progress.

I thank Marco Madrigal and Melissa Montero at RidgeRun, for contributing professional management over the dispTEC2 project, as well as providing me with valuable lessons during one of the hardest points in my life thus far.

I thank those brilliant minds I've worked with at RidgeRun, which have trained me in the art of developing all sorts of software shenanigans.

I thank Pablo Alvarado, for contributing his extensive personal expertise, his time and patience, his enthusiasm for understanding, his natural talent as an instructor, his steady push to bring out the most of me, and his nerdy jokes.

\vspace*{1cm}

\thesisAuthor

Cartago, \today

\cleardoublepage

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "paMain"
%%% End: 
