\documentclass[12pt,oneside]{book}
\usepackage[letterpaper, total={19cm, 20cm}]{geometry}

\usepackage{graphicx}
\usepackage{csquotes}
\usepackage[backend=biber,              % Use biber/biblatex
            style=ieee,
            sorting=none,
            citestyle=numeric-comp]{biblatex}
\usepackage{array, multirow}
\usepackage{caption}
\usepackage{subcaption}

\addbibresource{../tesis/literatura.bib}
\input{../tesis/code_blocks.tex}


\begin{document}
 \graphicspath{{./}{../tesis/fig/}}
  Tecnológico de Costa Rica
  \par\vspace{1mm}
  Escuela de Ingeniería Electrónica
  \par\vspace{1mm}
  Programa de Licenciatura en Ingeniería Electrónica
  \par\vspace{10mm}
  Trabajo Final de Graduación
  \par\vspace{1mm}
  Francis Guindon Badilla
  \par\vspace{1mm}
  2018259419
  \par\vspace{10mm}
  \large\textbf{Bitácora - Semana 3}
  \par\vspace{10mm}
  \small

  \begin{table} [!h]
    \centering
    \small
    \begin{tabular}{p{1.5 cm} p{2.1 cm} p{5 cm} p{8 cm}}
      \hline
      Fecha & Duración & Actividad & Descripción \\
      \hline
      22/2/23 & 1 h & Reunión de avance 2 & Metas: Terminar de coleccionar videos para dataset, Preguntar a Greivin sobre generación de ground truths (cómo usaba el histograma), Ajustar Ranger para pasarle datos por API (NO DEDICAR DEMASIADO TIEMPO A CAMBIAR EL API), Tener ejemplo con features generados \\
      23/2/23 & 1:16 PM - & Coleccionar videos & \\
      \hline
      \textbf{Total} & 21 h \\
      \hline
    \end{tabular}
  \end{table}
  
  \vfill

  \begin{tabular}{p{3 cm} p{10 cm}}
    Firma profesor: & \\
    \cline{2-2}
  \end{tabular}

  \newpage

  \section{Notas}
  \setlength\parindent{0pt}

  I have 5 goals for this week:
  \begin{enumerate}
    \item Complete dataset
    \item Investigate ground truth generation (ask Greivin)
    \item Adjust Ranger to recieve data from API
    \item Complete feature generation
    \item Train example
  \end{enumerate}

  To complete my first goal:
  \begin{enumerate}
    \item Review anteproyecto goals
    \item Determine what kind of videos I want
    \item Find videos on the internet
    \item Download videos
    \item Verify that they work with the data generation pipeline
  \end{enumerate}

  According to the anteproyecto, videos must contain:
  \begin{enumerate}
    \item 6 different activities
    \item 3 different light conditions
    \item at least 600 frames long each
    \item at least 1280x720 resolution each
  \end{enumerate}

  What do I already have?
  \begin{enumerate}
    \item \lstinline| SOS_20220204_122232.MOV |
    \item \lstinline| VID_20220220_152529.MOV |
    
    These 2 videos are Marco's daytime dashcam recordings.

    \item \lstinline| MOVI6859.mp4 |
    
    ...

    \item \lstinline| MOVI6871.mp4 |
    
    These 13 videos are Marco's nighttime dashcam recordings.
  \end{enumerate}

  This means I have:
  \begin{itemize}
    \item 1 activity category (Driving)
    \item 2 lighting conditions (Daytime and Nightime)
    \item Much more than 600 frames each (20 seconds at 30 fps)
    \item 720p videos
  \end{itemize}
  
  According to my rules, I need videos in 1 more lighting condition, and 5 more activities.

  These are the 6 activities I have in mind:
  \begin{itemize}
    \item Urban scenery while driving (the one I already have)
    \item Nature scenery while walking
    \item Sidewalk scenery while walking
    \item People in Sports
    \item People Dancing
    \item People Video conferencing
  \end{itemize}

  I found the BOSS dataset \cite{Velastin2017}. Turns out, the resolution is not
  right. This dataset explored certain activities in trains, like burglary. It might have been an interesting direction for the proyecto if it happens to have high metrics in certain datasets.

  I found \url{https://research.google.com/youtube8m/explore.html}.
  It helps explore youtube videos in a certain category.
  I used it once, and found the recomendations had low quality.
  I decided to directly search into youtube: `hd video walking'
  The first option at the time (03:36 P.M. 23/2/23): 4K VIDEO ULTRA HD - VALENCIA, SPAIN | 4K Walking Tour - Relax Video
  I watched it a while.
  The camareographer came out of an elevator to a white wall.
  He turn to a door.
  He goes out on a street with lots of people.
  The camareographer experiences a variety of scenes and people engaging in different activities.
  The video is 1.75 H long.
  I could't have asked for a better dataset (¿Or so I think ... ?)
  Well, It will work great for now.
  I google searched `download youtube video'.
  I clicked on \url{https://ssyoutube.com/en37/youtube-video-downloader}.
  I inputed the video link: \url{https://www.youtube.com/watch?v=EpCvEgh3I7o}.
  I downloaded the one titled 720.mp4:
    720: Minimum resolution in Anteproyecto
    mp4: is mpeg-4, which uses h264x video encoding (Just what I need :).
  Using vlc, it's the real deal, it doesn't seem to be compressed beyond h264x.
  I want to chop it up into samples between specific ranges.
  First, I'll rename the videos to simplify their identification.
  I'll use a readme to keep track of the original name (in case I need it) and a
  description of the video contents.

partial\_sort


  \printbibliography[title={Bibliografía},heading=bibintoc]
\end{document}
